Conference Paper Critique

### 2019-03-30 conf_paper/paper.tex
new measurements and paper update

\begin{table}[!ht]
    \begin{center}
        \begin{tiny}
        	\setlength{\tabcolsep}{.9\tabcolsep}
            \begin{tabular}{cc|c|c|c|c|c|c|}           
                \cline{3-8}
                && \multicolumn{3}{c|}{Jitter Standard Deviation (ns)} & \multicolumn{3}{c|}{Max. Time Interval Error. (ns)} \T\\
                \cline{3-8} 
                &&PLL 11&PLL 12&PLL 22&PLL 11&PLL 12&PLL 22\T\\
                \hline
                \multicolumn{2}{|l|}{Osc 1, PDET A}&-&-&-&-&-&-\T\\
                \multicolumn{2}{|r|}{Free PLLs} &1.4377 &1.4714&1.4217  &6.1910&6.3667&6.8052 \T\\
                \multicolumn{2}{|r|}{Uni-dir.}  &0.91589&1.0993&1.0875  &8.3619&8.9768&10.974 \T\\
                \multicolumn{2}{|r|}{Bi-dir.}   &1.0470 &1.0979&1.0306  &24.998&33.767&33.204 \T\\
                \hline
                \multicolumn{2}{|l|}{Osc 2, PDET A}&-&-&-&-&-&-\T\\
                \multicolumn{2}{|r|}{Free PLLs} &78.458&74.025&67.779  &146.09&143.70&142.03 \T\\
                \multicolumn{2}{|r|}{Uni-dir.}  &78.428&72.646&65.665  &146.23&298.49&200.10 \T\\
                \multicolumn{2}{|r|}{Bi-dir.}   &78.436&73.827&67.648  &235.73&497.60&311.28 \T\\
                \hline
                \multicolumn{2}{|l|}{Osc 2, PDET B}&-&-&-&-&-&-\T\\
                \multicolumn{2}{|r|}{Free PLLs} &7.8090&7.8827&6.6272   &17.336&21.151&24.302 \T\\
                \multicolumn{2}{|r|}{Uni-dir.}  &7.7866&8.1145&7.3598   &17.649&29.962&37.051 \T\\
                \multicolumn{2}{|r|}{Bi-dir.}   &7.7575&7.7729&6.6962   &30.019&40.577&45.617 \T\\
                \hline
                \B
            \end{tabular}
        \end{tiny}
        \caption{}
        \label{table:b_c_perf}
    \end{center}
\vspace{-0.5cm}
\end{table}
It is apparent that the combination of the inverter chain DCO and the FPGA clocked phase detector is an ill advised choice, with the system's jitter being an order of magnitude worse than the design using inverter delay based detector. In order to obtain measurements for this combination, due to the poor performance, a four times divider was inserted into the feedback path and the comparison made between this divided output and a reference signal at 1.25 MHz, and hence the presence of jitter greater than the period of 200 ns. In this system, the FPGA clock is at 258 MHz, the maximum possible to satisfy timing requirements, thus giving a detection resolution of 3.875 nanoseconds. This is significantly greater than the 1.2 nanosecond period step of the oscillator, requiring an increase in the loop filter gains when compared to the first combination in the table. The problems of relatively inaccurate detection and increased gains combine to produce a system that is only able to achieve poor locking performance. In case three then the detector's resolution improves to 0.6 nanoseconds and produces relatively good system performance. This combination does not perform as well as that of case one, but that is attributable to the unrealistic nature of the FPGA clocked design. Both case one and three work well, delivering a level of jitter that is both low yet allows an indication of how impactful variations in architecture or control parameters are to be seen visually on an oscilloscope with appropriate persistence.\\

@@

\begin{figure}[h]%
    \centering
    \subfloat[Inverter Based Design.]{{\includegraphics[width=0.5\linewidth]{distrib_ring} }}%
    \subfloat[FPGA Clocked Design.]{{\includegraphics[width=0.5\linewidth]{distrib_pa} }}%
    \caption{Example Distribution of Periods.\label{fig:dists}}    
    \vspace{-0.5cm}
\end{figure}
%\begin{figure}[h]
%   \centering
%   \subfloat[FPGA Clocked Design][width=0.25\textwidth]{distrib_pa}
%   \caption{Distribution of Periods.}
%   \label{fig:dist2}
%\end{figure}
Figure \ref{fig:dists} paints a picture of the unrealistic nature of the FPGA clocked design in comparison to its inverter based counterpart, each oscillator will have identical intrinsic period steps thus eliminating any jitter that maybe be seen in the system due to misalignment. This effects the suitability of the FPGA clocked designs for the improvement of simulation models, or the examination of how a novel block may impact the behaviour of the network.
\section*{Conclusion}
An FPGA is a suitable environment for the prototyping of ADPLL networks and can fill a number of roles depending on the designer's requirements. However, the designer should bear in mind the platform's limitations, especially when attempting to use a frequency that is not orders of magnitude lower than the maximum clock available from the FPGA's clock manager. Inverter based and FPGA clocked designs, both have a niche in which they are the preferred option, with the clocked design better suiting replication of an existing design at scaled-down frequencies and the inverter based designs better in the modelling and analysis of ADPLL network behaviour.

\end{document}

>>>>

\begin{table}[!ht]
    \begin{center}
        \begin{tiny}
        	\setlength{\tabcolsep}{.9\tabcolsep}
            \begin{tabular}{cc|c|c|c|c|c|c|}           
                \cline{3-8}
                && \multicolumn{3}{c|}{Jitter Standard Deviation (ns)} & \multicolumn{3}{c|}{Max. Time Interval Error. (ns)} \T\\
                \cline{3-8} 
                &&PLL 11&PLL 12&PLL 22&PLL 11&PLL 12&PLL 22\T\\
                \hline
                \multicolumn{2}{|l|}{Osc 1, PDET A}&-&-&-&-&-&-\T\\
                \multicolumn{2}{|r|}{Free PLLs} &1.4377 &1.4714&1.4217  &6.1910&6.3667&6.8052 \T\\
                \multicolumn{2}{|r|}{Uni-dir.}  &0.91589&1.0993&1.0875  &8.3619&8.9768&10.974 \T\\
                \multicolumn{2}{|r|}{Bi-dir.}   &1.0470 &1.0979&1.0306  &24.998&33.767&33.204 \T\\
                \hline
                \multicolumn{2}{|l|}{Osc 2, PDET A}&-&-&-&-&-&-\T\\
                \multicolumn{2}{|r|}{Free PLLs} &0.56728&0& 0&5.3797&0&0 \T\\
                \multicolumn{2}{|r|}{Uni-dir.}  &0.57365&0& 0&6.0632&0&0 \T\\
                \multicolumn{2}{|r|}{Bi-dir.}   &0.58760&0& 0&15.466&0&0 \T\\
                \hline
                \multicolumn{2}{|l|}{Osc 2, PDET B}&-&-&-&-&-&-\T\\
                \multicolumn{2}{|r|}{Free PLLs} &0.71635&0&0  &4.8293&0&0 \T\\
                \multicolumn{2}{|r|}{Uni-dir.}  &0.76883&0&0  &4.7922&0&0 \T\\
                \multicolumn{2}{|r|}{Bi-dir.}   &0.79292&0&0  &6.5277&0&0 \T\\
                \hline
                \B
                %% old 2b
                %&7.8090&7.8827&6.6272   &17.336&21.151&24.302
                %&7.7866&8.1145&7.3598   &17.649&29.962&37.051
                %&7.7575&7.7729&6.6962   &30.019&40.577&45.617
                %% old 2a
                %&78.458&74.025&67.779  &146.09&143.70&142.03
                %&78.428&72.646&65.665  &146.23&298.49&200.10
                %&78.436&73.827&67.648  &235.73&497.60&311.28

                %&5.6728e-10&0&0&5.3797e-09&0&0
                %&5.7365e-10&0&0&6.0632e-09&0&0
                %&5.8760e-10&0&0&1.5466e-08&0&0

            \end{tabular}
        \end{tiny}
        \caption{}
        \label{table:b_c_perf}
    \end{center}
\vspace{-0.5cm}
\end{table}
From the table it is apparent that the coarser period and detection steps of Design ``1A''  (3.875 nanoseconds as at greater clock frequencies timing violations would occur) cannot deliver the same jitter performance as the inverter ring driven designs. Looking at the two subsequent designs their lesser flexibility is made up for by their more realistic jitter behaviour. As would be expected best performance occurs when the network is in PLL mode and as the quality of the reference degrades as the network is connected up performance becomes worse. In terms of cycle-to-cycle jitter the best performing design is that of ``2A'', however, its time interval error is significantly worse especially in bilateral network mode. This more aggressive degradation as the network is linked up can be attributed to the worse detection resolution of the FPGA clocked phase detector, four times worse than the 1.2 second step of the entirely inverter based Design ``2B''.\\
The further a PLL is away from the reference feeding ADPLL 11 the worse performance is, peaking furthest from the reference in ADPLL 22.
%TODO insert comment here when I have more oscillators for 1 lines or so.

The lesser cycle-to-cycle of Design ``2A'' follows from the implementation independent design of the phase detector. Unlike the inverter based design where the implementation may result in the propagation delay between taps on the delay line changing, from both tap to tap in the same detector and the same tap in different detectors, the clocked design has identical detection resolutions as each register is driven by the FPGA clock. This can be highlighted in the more easily demonstrable case of the clocked and inverter based oscillators.\\
\begin{figure}[h]%
    \centering
    \subfloat[Inverter Based Design.]{{\includegraphics[width=0.5\linewidth]{distrib_ring} }}%
    \subfloat[FPGA Clocked Design.]{{\includegraphics[width=0.5\linewidth]{distrib_pa} }}%
    \caption{Example Distribution of Periods.\label{fig:dists}}    
    \vspace{-0.5cm}
\end{figure}
Figure \ref{fig:dists} paints a picture of the unrealistic nature of the FPGA clocked design in comparison to its inverter based counterpart, each oscillator will have identical intrinsic period steps thus eliminating any jitter that maybe be seen in the system due to misalignment. This effects the suitability of the FPGA clocked designs for the improvement of simulation models, or the examination of how a novel block may impact the behaviour of the network.
\section*{Conclusion}
An FPGA is a suitable environment for the prototyping of ADPLL networks and can fill a number of roles depending on the designer's requirements. However, the designer should bear in mind the platform's limitations, especially when attempting to use a frequency that is not orders of magnitude lower than the maximum clock available from the FPGA's clock manager. Inverter based and FPGA clocked designs, both have a niche in which they are the preferred option, with the clocked design better suiting replication of an existing design at scaled-down frequencies and the inverter based designs better in the modelling and analysis of ADPLL network behaviour.

\end{document}
%It is apparent that the combination of the inverter chain DCO and the FPGA clocked phase detector is an ill advised choice, with the system's jitter being an order of magnitude worse than the design using inverter delay based detector. In order to obtain measurements for this combination, due to the poor performance, a four times divider was inserted into the feedback path and the comparison made between this divided output and a reference signal at 1.25 MHz, and hence the presence of jitter greater than the period of 200 ns. In this system, the FPGA clock is at 258 MHz, the maximum possible to satisfy timing requirements, thus giving a detection resolution of 3.875 nanoseconds. This is significantly greater than the 1.2 nanosecond period step of the oscillator, requiring an increase in the loop filter gains when compared to the first combination in the table. The problems of relatively inaccurate detection and increased gains combine to produce a system that is only able to achieve poor locking performance. In case three then the detector's resolution improves to 0.6 nanoseconds and produces relatively good system performance. This combination does not perform as well as that of case one, but that is attributable to the unrealistic nature of the FPGA clocked design. Both case one and three work well, delivering a level of jitter that is both low yet allows an indication of how impactful variations in architecture or control parameters are to be seen visually on an oscilloscope with appropriate persistence.\\

@@
